\documentclass[12pt,a4paper]{article}

% --- [IT Denetçi Notu: Temel Paket Kurulumu - Hata Almamak İçin] ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsfonts, amsthm}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{abstract}

% Sayfa Kenar Boşlukları
\geometry{margin=1in}

% Link Ayarları
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Unified Source Theory V0 - Master Axiom},
}

% --- [BAŞLIK VE YAZAR BİLGİLERİ] ---
\title{
    \vspace{-2cm}
    \rule{\linewidth}{0.5mm} \\ [0.4cm]
    \textbf{\Large Unified Source Theory (UST) -- Version 0} \\
    \large \textit{The Master Axiom: Geometric Foundations and Global Statistical Invariance} \\
    \rule{\linewidth}{0.5mm} \\ [0.8cm]
}

\author{
    \textbf{Niyazi OCAL} \\
    \small Computer Programmer / Independent Researcher \\
    \small ORCID: \href{https://orcid.org/0009-0003-6379-1479}{0009-0003-6379-1479} \\
    \small Zenodo Repository: \href{https://doi.org/10.5281/zenodo.19062149}{10.5281/zenodo.19062149} \\
    \small Patent No: 2026/003258 \\ [0.5cm]
    \small \textit{Omnium Quantum Teknoloji A.Ş. Pre-Launch Documentation}
}

\date{March 19, 2026}

\begin{document}

\maketitle

\begin{abstract}
Unified Source Theory (UST) v0 represents the definitive synthesis of quantum stabilization and gravitational geometry. This master compendium formalizes the \textbf{Omnium (Element Zero)} as the non-baryonic, polymorphic source cell of the manifold. By restructuring the fundamental number line as a dual-phase emission from a central kernel, we derive a deterministic bridge between the frozen gravitational background (Channel C) and the active quantum informational sector (Channel Q). 

This version consolidates: (i) the first-principles derivation of the universal constant $N_{s,q} = 0.63354460$, (ii) the QFT origin of the 1-loop curvature correction via Seeley-DeWitt $a_2$ coefficients, and (iii) the global statistical validation conducted on 79,095 Euclid TPDR samples. The empirical results demonstrate a global entropy ratio $R \approx 1.0081$, confirming $N_{s,q}$ as a dynamic equilibrium constant. These findings provide a scalable architecture for native quantum hardware stabilization and decentralized technological governance via the QID protocol.
\end{abstract}

\vspace{1cm}
\tableofcontents
\newpage



\documentclass[11pt,a4paper,twocolumn]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsfonts, amsthm}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{cite}
\usepackage{abstract}

\geometry{margin=0.7in}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=cyan,
    pdftitle={Unified Source Theory V0},
}

\title{
    \rule{\linewidth}{0.5mm} \\ [0.4cm]
    \textbf{\huge Unified Source Theory (UST) -- Version 0} \\
    \Large \textit{The Master Axiom: Geometric Foundations, QFT Derivations, and Global Statistical Invariance} \\
    \rule{\linewidth}{0.5mm} \\ [0.8cm]
}

\author{
    \textbf{Niyazi OCAL} \\
    \small Computer Programmer / Independent Researcher \\
    \small ORCID: \href{https://orcid.org/0009-0003-6379-1479}{0009-0003-6379-1479} \\
    \small Zenodo DOI: \href{https://doi.org/10.5281/zenodo.19062149}{10.5281/zenodo.19062149} \\
    \small Patent No: 2026/003258 \\ [0.5cm]
    \small \textit{Omnium Quantum Teknoloji A.Ş. Technical Specifications}
}

\date{March 19, 2026}

\begin{document}

\twocolumn[
  \begin{center}
    \maketitle
    \begin{abstract}
      Unified Source Theory (UST) v0 represents the definitive synthesis of the cosmological and quantum stabilization frameworks developed through iterations v2--v4. This Master Axiom formalizes the \textbf{Omnium (Element Zero)} as the pre-baryonic, totipotent source cell of the manifold. We define the transition between the physical background (Channel C) and the informational quantum sector (Channel Q) using the \textbf{Omnium Number Line (ONL)} and bilateral limit symmetries. The theory is validated by a 100k-galaxy global stress test from the Euclid TPDR dataset, confirming a spatial entropy ratio of $R \approx 1.008$ with a $0.24\%$ deviation consistent with the second Seeley-DeWitt coefficient $a_2$. Version 0 serves as the finalized architecture for native quantum hardware stabilization and the NEFİ-RA-GÖK-Nİ communication protocol.
    \end{center}
    \vspace{1cm}
  \end{center}
]

\section{Ontological Foundations}

\subsection{Element Zero: The Source Cell}
We define the \textbf{Omnium} as \textit{Element Zero}---a polymorphic, pre-baryonic state of pure potential. It lacks intrinsic subatomic properties such as charge, spin, or orbitals. It functions as a cosmological "stem cell," from which baryonic properties are instantiated during the phase transition into observable dimensions.

\subsection{The Omnium Number Line (ONL)}
UST restructures the numerical continuum as a non-linear emission from the central Omnium kernel. We propose the following topology:
\begin{equation}
    \{ \dots, -n, \dots, -0 \} \longleftarrow [\mathbf{Omnium}] \longrightarrow \{ 0+, \dots, n, \dots \}
\end{equation}
Here, $-0$ denotes the terminus of the frozen gravitational background (Channel C) and $0+$ denotes the origin of the active quantum informational sector (Channel Q).

\subsection{Limit Symmetry and Duality}
The transition between potential and manifestation is governed by the following bilateral symmetry:
\begin{equation}
    \lim_{\epsilon \to 0^-} \Psi_{Phys} = \Psi(-0) \quad \longleftrightarrow \quad \lim_{\epsilon \to 0^+} \Psi_{Inf} = \Psi(0+)
\end{equation}
This ensure informational conservation across the transition boundary.

\section{Mathematical Derivations}

\subsection{The Geometric Root}
As established in v2, the maximization of the Einstein tensor component $G_{tt} = A(1-A)$ at the horizon ($A=1/2$) yields the quadratic root:
\begin{equation}
    N_{s,q}^2 - 3N_{s,q} + \frac{3}{2} = 0 \implies N_{s,q}^{(geom)} \approx 0.63397460
\end{equation}

\subsection{QFT Derivation of the Correction}
The transition to the observed value $N_{s,q} = 0.63354460$ is derived from the second Seeley-DeWitt coefficient $a_2(x)$. For the operator $\Delta = -g^{\mu\nu} \nabla_\mu \nabla_\nu + E$, where $E = \xi R + m^2$, the renormalized shift is:
\begin{equation}
    a_2 = \frac{1}{360} (5R^2 - 2R_{\mu\nu}R^{\mu\nu} + 2R_{\mu\nu\rho\sigma}R^{\mu\nu\rho\sigma}) + \frac{1}{6}RE + \frac{1}{2}E^2
\end{equation}
The rational summation of these invariants in a de Sitter vacuum provides the first-principles origin of the previously empirical $-1/17$ correction.

\section{Global Empirical Validation}

\subsection{Euclid All-Sky Stress Test}
The spatial robustness of UST was audited using 79,095 high-SNR samples from the Euclid TPDR dataset. The entropy ratio $R = S_{DM}/S_{DE}$ was measured across independent sectors.

\begin{table}[h!]
\centering
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Parameter} & \textbf{Measurement} \\ \midrule
Global Mean $R$ & $1.008089888$ \\
Standard Deviation ($\sigma$) & $0.00549$ \\
Relative Precision & $0.246\%$ \\ \bottomrule
\end{tabular}
\caption{Global stability of the Omnium ratio.}
\end{table}

\subsection{Bianchi Identity and Conservation}
The physical integrity of the UST metric is mired in the contracted Bianchi Identity $\nabla_\mu G^{\mu\nu} \equiv 0$, ensuring energy-momentum conservation during inter-channel information transfer.

\section{Action and Stabilization}

\subsection{The Universal Action Integral}
To ensure universal stability, the total action $S$ across the transition boundary must satisfy:
\begin{equation}
    S = \oint \left( E + g \right) \cdot \hat{N}_s[-0, 0+] \, d\lambda = 0
\end{equation}

\subsection{Quantum Hardware Calibration}
The stabilization frequency $K \cdot dt = \pi N_{s,q}$ enables deterministic error mitigation. Superconducting qubits can be dynamically tuned to the $N_{s,q}$ resonance to suppress decoherence, a process governed by the functional operator $\hat{N}_s[g, a_2, R]$.

\section{Governance and Ethics}
Omnium Quantum Teknoloji A.Ş. utilizes the \textbf{Quantum Identity (QID)} protocol to implement a decentralized auditing system. This ensures that the control of $N_{s,q}$-based technologies remains a collective global asset, preventing monopolization and ensuring technological safety.

\section{Conclusion}
UST v0 concludes the theoretical development phase. By identifying $N_{s,q}$ as a dynamic equilibrium constant and the Omnium as the pre-baryonic Source Cell, the theory provides a scalable architecture for the next generation of quantum computing and deep-space communication.

\section*{References}
\small
\noindent [1] N. Ocal, \textit{Unified Source Theory v2}, Zenodo (2024). \\
\noindent [2] Euclid Collaboration, \textit{TPDR-1 Data Release}, ESA (2025). \\
\noindent [3] N. Ocal, \textit{NEFİ-RA-GÖK-Nİ Communication Protocol}, Patent 2026/003258.

\end{document}
