\documentclass[11pt,a4paper]{article}

% --- [PAKETLER] ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{hyperref}

\geometry{margin=1in}

% Python Kod Görünümü Ayarları
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue},
    stringstyle=\color{red},
    commentstyle=\color{green!50!black},
    showstringspaces=false,
    frame=single,
    breaklines=true
}

\begin{document}

% --- [BAŞLIK] ---
\begin{center}
    \textbf{\huge Type 1 Civilization Research} \\
    \vspace{0.2cm}
    \large Fundamental Sciences, Quantum \& AI Collective \\
    \vspace{0.5cm}
    \rule{\linewidth}{0.2mm} \\
    \vspace{0.3cm}
    \textbf{INAUGURAL MANIFESTO: SEARCHING FOR THE STABILIZATION CODE} \\
    \rule{\linewidth}{0.2mm}
\end{center}

\vspace{0.5cm}

% --- [GİRİŞ] ---
\section*{A Common Path for Independent Research}
My name is \textbf{Niyazi OCAL}. I am a computer programmer and system auditor with 35 years of experience in the IT sector (est. 1996). I hold no institutional academic titles; I am an \textbf{Independent Researcher} who has spent the last decade investigating the fundamental logic governing our universe.

This collective is founded on a single premise: The transition from a Type 0 to a \textbf{Type 1 Civilization} requires us to stop viewing the cosmos as a collection of random particles and start understanding it as a stabilized information system.

% --- [UST V0 ÖZETİ] ---
\section*{The Mission: Unified Source Theory (UST)}
Through the framework of \textbf{Unified Source Theory (UST)}, I have identified a universal dimensionless constant, $N_{s,q} = 0.63354460$, which acts as the system's "Master Checksum." This is not a heuristic guess; it is a mathematical necessity verified by:
\begin{itemize}
    \item \textbf{CERN ATLAS Data:} 10,000 high-energy events confirming stabilization rates.
    \item \textbf{ESA Euclid TPDR:} A global stress test of 79,095 galaxies confirming an entropy ratio $R \approx 1.008$ with only $0.24\%$ variance.
\end{itemize}

% --- [OMNIUM KODU] ---
\section*{The Source Code: Initial Vector}
In software terms, we model the origin of the manifold (The Omnium) as a pre-quantized state of infinite potential. Every computation in this group begins with the initialization of the Source:

\begin{lstlisting}
import numpy as np

# System Boot: Defining the Omnium (Element Zero)
# A state of pure potential prior to functional boundaries.
O = np.array([[np.inf, np.inf], [np.inf, np.inf]])

# Quantization via Nsq Operator:
# Results in the deterministic physical constants observed.
\end{lstlisting}

% --- [PRENSİPLER] ---
\section*{Our Protocol}
\begin{enumerate}
    \item \textbf{Popperian Falsifiability:} We do not seek dogmatic truths. We present rigid, parameter-free limits. If the data refutes the constant, the theory is discarded.
    \item \textbf{System Audit Disipline:} We apply the rigor of ISO 27001 and high-performance computing to the laws of physics.
    \item \textbf{Collective Intelligence (QID):} This technology is too critical to be monopolized. We propose a decentralized auditing system where every "Quantum Identity" (QID) contributes to the verification of the $S=0$ action balance.
\end{enumerate}

\vspace{0.5cm}

\section*{Join the Audit}
Whether you are a physicist, a developer, or a curious mind, you are welcome. Let us stop patching the "noise" and start resonating with the "Source."

\vspace{1cm}

\begin{flushleft}
    \textbf{Niyazi OCAL} \\
    Founder, Omnium Quantum Teknoloji A.S. (Pre-Launch) \\
    ORCID: 0009-0003-6379-1479 \\
    Patent No: 2026/003258 \\
    \href{https://doi.org/10.5281/zenodo.19062149}{Zenodo Repository}
\end{flushleft}

\end{document}